Formulating Regional Typologies

### 2023-11-01 regional_typologies.qmd
add a slide from FJ

---
title: "Formulating Regional Typologies"
author: "Dony Indiarto, Mohamad Nugraha"
affiliation: "CIFOR-ICRAF Indonesia"
project:
  type: website
  output-dir: docs
format: 
  revealjs:
    theme: simple
    scrollable: true
    embed-resources: true
reference-location: document
editor: visual
---

## Agenda

1.  Understanding the Regional Typologies
2.  Methodology and Steps
3.  Case Studies and Examples
4.  Closing Remarks

>>>>

---
title: "Formulating Regional Typologies"
author: "CIFOR-ICRAF Indonesia"
date: last-modified
date-format: "dddd MMM D, YYYY"
project:
  type: website
  output-dir: docs
format: 
  revealjs:
    theme: simple
    scrollable: true
    embed-resources: true
reference-location: document
editor: visual
---

## Agenda
0.  Background Context
1.  Understanding the Regional Typologies
2.  Methodology
3.  Case Studies
4.  Closing Remarks

-----------------------------------------------------------------------
## Application of Typology in the Development Masterplan for Integrated Land and Seascape

- The development of an integrated land and sea masterplan (green economic growth)  is structured around planning units.

- Each planning unit is defined by a range of specific characteristics, derived from multiple layers of spatial data.

- The concept of "Regional Typology" identifies common characteristics—whether in villages, districts, or special units—that guide the formulation of both planning units and strategy or intervention recommendations.

- The planning process involves a continuous flow of data and information from macro to meso to micro levels, and vice versa.

- The masterplan will include a range of tailored strategies and on-site interventions, reflecting the specific needs of each planning unit.
------------------------------------------------------------------------
